---
title: "Lab7"
author: "Andrea Bruzzone, Thomas Zhang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r,message=FALSE,echo=FALSE}
library(Lab7)
library(caret)
library(mlbench)
data(BostonHousing)
```


```{r, echo=FALSE}
inTrain <- createDataPartition(y=BostonHousing$crim,
                               p=.90,
                               list=FALSE)

training <- BostonHousing[inTrain,]
testing <- BostonHousing[-inTrain,]

lmfit <- train(crim ~.,
               data = training,
               method ="lm",
               preProc = c("center","scale"))

lmforwardfit <- train(crim ~.,
               data = training,
               method ="leapForward",
               preProc = c("center","scale"))

str(lmfit)
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
